\documentclass[../main.tex]{subfiles}
\begin{document}
\begin{thebibliography}{99}
\bibitem{mongodb2024} MongoDB, Inc., \textit{The MongoDB 7.0 Manual}. [Online]. Available: \url{https://www.mongodb.com/docs/manual/} (visited on 12/27/2024).

\bibitem{nodejs2024} OpenJS Foundation, \textit{Node.js Documentation}. [Online]. Available: \url{https://nodejs.org/docs/latest/api/} (visited on 12/27/2024).

\bibitem{haerder1983principles} T. Haerder and A. Reuter, ``Principles of transaction-oriented database recovery,'' \textit{ACM Computing Surveys}, vol. 15, no. 4, pp. 287-317, 1983.

\bibitem{brewer2012cap} E. Brewer, ``CAP twelve years later: How the rules have changed,'' \textit{Computer}, vol. 45, no. 2, pp. 23-29, 2012.
\bibitem{coulouris2011distributed} G. Coulouris, J. Dollimore, T. Kindberg, and G. Blair, \textit{Distributed Systems: Concepts and Design}, 5th Edition. Addison-Wesley, 2011.
\bibitem{Sivarajah2017} U. Sivarajah, M. Kamal, Z. Irani, and V. Weerakkody, "Critical analysis of Big Data challenges and analytical methods," \textit{Journal of Business Research}, vol. 70, no. 1, pp. 263–286, Jan. 2017.

\bibitem{Azar2014} A. Azar and A. Hassanien, "Dimensionality reduction of medical big data using neural-fuzzy classifier," \textit{Soft Computing}, vol. 19, no. 4, pp. 1115–1127, June 2014.

\bibitem{Nega2017} A. Nega and A. Kumlachew, "Data Mining Based Hybrid Intelligent System for Medical Application," \textit{International Journal of Information Engineering and Electronic Business}, vol. 9, no. 4, pp. 38–46, 2017.

\bibitem{Ray2014} P. K. Ray, S. R. Mohanty, N. Kishor, and J. P. S. Catalao, "Optimal feature and decision tree-based classification of power quality disturbances in distributed generation systems," \textit{IEEE Transactions on Sustainable Energy}, vol. 5, no. 1, pp. 200–208, Jan. 2014.

\bibitem{White2012} T. White, \textit{Hadoop: The Definitive Guide}, O'Reilly Media Inc./Yahoo Press, 2012.

\bibitem{Corbett2013} J. Corbett, P. Hochschild, W. Hsieh, S. Kanthak, E. Kogan, H. Li, A. Lloyd, et al., "Spanner: Google’s globally distributed database," \textit{ACM Transactions on Computer Systems}, vol. 31, no. 3, pp. 1–22, 2013.

\bibitem{Linoff2011} G. S. Linoff and M. J. A. Berry, \textit{Data Mining Techniques: For Marketing, Sales, and Customer Relationship Management}, 3rd ed., pp. 23–29, 2011.

\bibitem{Abraham2013} L. Abraham, S. Subramanian, J. Wiener, O. Zed, J. Allen, O. Barykin, et al., "Scuba: Diving into data at Facebook," \textit{Proceedings of the VLDB Endowment}, vol. 6, no. 11, pp. 1057–1067, 2013.

\bibitem{Lee2012} G. Lee, J. Lin, C. Liu, A. Lorek, and D. Ryaboy, "The unified logging infrastructure for data analytics at Twitter," \textit{Proceedings of the VLDB Endowment}, vol. 5, no. 12, pp. 1771–1780, 2012.

\bibitem{Siewert2013} S. B. Siewert, "Big data in the cloud - Data velocity, volume, variety, and veracity," 2013.

\bibitem{Sammer2012} E. Sammer, \textit{Hadoop Operations}, O'Reilly Media, Sept. 2012.

\bibitem{Breiman2001} L. Breiman, "Random forests," \textit{Machine Learning}, vol. 45, no. 1, pp. 5–32, Oct. 2001.

\bibitem{Rendon2011} E. Rendón, I. Abundez, A. Arizmendi, and E. M. Quiroz, "Internal versus external cluster validation indexes," \textit{Pattern Recognition Letters}, vol. 5, no. 1, pp. 27–33, 2011.

\bibitem{Bernard2012} S. Bernard, S. Adam, and L. Heutte, "Dynamic random forests," \textit{Pattern Recognition Letters}, vol. 33, no. 12, pp. 1580–1586, Sept. 2012.

\bibitem{Pfitzner2009} D. Pfitzner, R. Leibbrandt, and D. M. W. Powers, "Characterization and evaluation of similarity measures for pairs of clusterings," \textit{Knowledge and Information Systems}, vol. 19, no. 3, pp. 361–394, 2009.

\bibitem{Halkidi2001} M. Halkidi, Y. Batistakis, and M. Vazirgiannis, "On clustering validation techniques," \textit{Journal of Intelligent Information Systems}, vol. 17, no. 2–3, pp. 107–145, 2001.

\bibitem{Frank2017} E. Frank, M. A. Hall, and I. H. Witten, \textit{Data Mining: Practical Machine Learning Tools and Techniques}, 4th ed., pp. 7–9, 2017.

\bibitem{Spark2016} A. Spark, "Spark MLlib - random forest," 2016. [Online]. Available: \url{http://spark.apache.org/docs/latest/mllib-ensembles.html}

\bibitem{Karau2015} H. Karau, A. Konwinski, P. Wendell, and M. Zaharia, \textit{Learning Spark: Lightning-Fast Big Data Analysis}, O'Reilly Media, 2015.

\bibitem{Luu2017} H. Luu, \textit{Beginning Apache Spark 2: With Resilient Distributed Datasets, Spark SQL, Structured Streaming and Spark Machine Learning library}, pp. 51–55, 2017.

\bibitem{Chambers2018} B. Chambers and M. Zaharia, \textit{Spark: The Definitive Guide}, pp. 20–28, 2018.
\bibitem{hochreiter1997lstm} S. Hochreiter and J. Schmidhuber, ``Long Short-Term Memory,'' \textit{Neural Computation}, vol. 9, no. 8, pp. 1735–1780, 1997. [Online]. Available: \url{https://www.bioinf.jku.at/publications/older/2604.pdf} (visited on 04/28/2025).

\bibitem{lecun1998gradient} Y. LeCun, L. Bottou, Y. Bengio, and P. Haffner, ``Gradient-based learning applied to document recognition,'' \textit{Proceedings of the IEEE}, vol. 86, no. 11, pp. 2278–2324, 1998. [Online]. Available: \url{http://yann.lecun.com/exdb/publis/pdf/lecun-98.pdf}.

\bibitem{radford2021clip} A. Radford, J. W. Kim, C. Hallacy, A. Ramesh, G. Goh, S. Agarwal, G. Sastry, A. Askell, P. Mishkin, J. Clark, et al., ``Learning Transferable Visual Models From Natural Language Supervision,'' in \textit{Proceedings of the 38th International Conference on Machine Learning (ICML 2021)}, vol. 139, pp. 8748–8763. [Online]. Available: \url{https://arxiv.org/abs/2103.00020}.
\bibitem{vaswani2017attention} A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, Ł. Kaiser, and I. Polosukhin, ``Attention Is All You Need,'' in \textit{Proceedings of the 31st International Conference on Neural Information Processing Systems (NeurIPS 2017)}, vol. 30. Curran Associates, Inc., 2017. [Online]. Available: \url{https://arxiv.org/abs/1706.03762}.

\bibitem{krizhevsky2012imagenet} A. Krizhevsky, I. Sutskever, and G. E. Hinton, ``ImageNet Classification with Deep Convolutional Neural Networks,'' in \textit{Proceedings of the 25th International Conference on Neural Information Processing Systems (NeurIPS 2012)}, vol. 1, pp. 1097–1105. 2012. [Online]. Available: \url{https://papers.nips.cc/paper_files/paper/2012/hash/c399862d3b9d6b76c8436e924a68c45b-Abstract.html}.

\end{thebibliography}

\end{document}